Supplementary Material

### 2021-12-21 supplement/supplement_docx.Rmd
fixing scripts - CD revision 1

---
title: "Supplementary Material"
subtitle: "*Can real-world stimuli improve cognitive performance for children living in adversity?*"
output:
   bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: false
    lof: yes
    toc: false
    extra_dependencies: ["booktabs","caption","longtable","float"]
    keep_tex: true
geometry: margin=.5in
mainfont: Times
fontsize: 11pt
urlcolor: blue
header-includes:
- \usepackage{siunitx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', fig.pos = "H", fig.show = 'asis')

library(tidyverse)
library(gt)

load("staged-objects.Rdata")
```

@@

```{r sitables1, results='asis'}
si_table.01.1 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

@@

```{r sifig1, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_unp
```

@@

```{r sifig2, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_vio
```

@@

```{r sifig3, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_ses
```

@@

```{r sifig4, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_unp
```

@@

```{r sifig5, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_vio
```

@@

```{r sifig6, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_ses
```

@@

For tables of all median effects and simple effects:

@@

@@

@@

```{r sitables2, results='asis'}
si_table.02.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

@@

```{r sitables3, results='asis'}
si_table.03.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

@@

```{r sifig7, fig.width=8, fig.height=7.5, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
unp_shifting
```

@@

```{r sifig8, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_shifting
```

@@

```{r sifig9, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_shifting
```

@@

```{r sifig10, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
unp_updating
```

@@

```{r sifig11, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_updating
```

@@

```{r sifig12, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_updating
```

@@

```{r sitables4, results='asis'}
si_table.04.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

@@

```{r sitables5, results='asis'}
si_table.05.0 %>%
  as_latex() %>%
  as.character() %>%
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>%
  cat()
```

>>>>

---
title: "Supplementary Material"
subtitle: "*Can real-world stimuli improve cognitive performance for children living in adversity?*"
output:
  officedown::rdocx_document:
    reference_docx: reference-doc.docx
    page_size:
      width: 8.5
      height: 11
      orient: "portrait"
    page_margins:
      bottom: .5
      top: .5
      right: .25
      left: .25
      header: 0
      footer: 0
      gutter: 0
    plots:
      align: center
      style: Normal
      caption:
        style: Image Caption
        pre: 'SI Figure '
        sep: '. '
    tables:
      caption:
        style: Table Caption
        pre: 'SI Table '
        sep: '. '
---

```{r setup, include=FALSE}
# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  fig.show = "asis",
  fig.width = 8, 
  fig.height = 7.5,
  dpi = 600,
  out.extra = "",
  message = FALSE,
  warning = FALSE
)

# load libraries
library(tidyverse)
library(officer)
library(flextable)

# load all data and objects
load("staged-objects.Rdata")

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)
```

@@

```{r sitables1}
si_table.01.1$`_data` %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
  add_row(.after = 6, "mod_term_label" = "Violence") %>% 
  add_row(.after = 12, "mod_term_label" = "Poverty") %>%
  select(-iv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 7, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,7,13), j = 1) %>% 
  padding(i = c(2:6, 8:12, 14:18), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(
    iv = "", mod_term_label = "Term", 
    empty1 = "", 
    ci_shifting = "95% CI", 
    ci_updating = "95% CI"
    ) %>% 
  add_header_row(
    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 18, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

```{r sifig1, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_unp
```

@@

```{r sifig2, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_vio
```

@@

```{r sifig3, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_ses
```

@@

```{r sifig4, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_unp
```

@@

```{r sifig5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_vio
```

@@

```{r sifig6, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_ses
```

@@

**For tables of all median effects and simple effects:**

@@

**For attention shifting plots:**

@@

**For working memory updating plots:**

@@

```{r sitables2}
si_table.02.0$`_data` %>% 
  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
  add_row(.after = 7, "mod_term_label" = "Violence") %>% 
  add_row(.after = 14, "mod_term_label" = "Poverty") %>%
  select(-iv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 8, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 15, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,8,15), j = 1) %>% 
  padding(i = c(2:7, 9:14, 16:23), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(
    iv = "", mod_term_label = " ", 
    empty1 = "", 
    ci_shifting = "95% CI", 
    ci_updating = "95% CI"
    ) %>% 
  add_header_row(
    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  align(i = 2, j = 1, align = "left", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 23, border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  set_table_properties(width = 1, layout = "autofit")
```

@@

```{r sitables3}
si_table.03.0$`_data` %>% 
  add_column(.after = 6,"empty1" = "") %>% 
  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
  add_row(.after = 11, "iv" = "Working Memory Updating") %>%
  select(-dv) %>% 
  flextable() %>% 
  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
  bold(i = c(1,12), j = 1) %>% 
  padding(i = c(2:11, 13:22), j = 1, padding.left = 10) %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "") %>% 
  add_header_row(
    values = c(" ", "Task Version", " ", "Adversity Exposure"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = c(11,22), border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  fontsize(size = 11, part = "body") %>%
  set_table_properties(width = 1, layout = "autofit")
```

@@

```{r sifig7, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
unp_shifting
```

@@

```{r sifig8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_shifting
```

@@

```{r sifig9, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_shifting
```

@@

```{r sifig10, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
unp_updating
```

@@

```{r sifig11, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_updating
```

@@

```{r sifig12, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_updating
```

@@

```{r sitables4}
si_table.04.0$`_data` %>% 
  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
  flextable() %>% 
  set_header_labels(
    iv = "", mod_term_label = " ", 
    empty1 = "", 
    ci = "95% CI"
  ) %>% 
  compose(i = 1, j = c(2), as_paragraph("\U1D6FD"), part = "header") %>% 
  compose(i = 1, j = c(4), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 1, j = c(5), as_paragraph("median ", as_i("N")), part = "header") %>% 
  fontsize(size = 11, part = "body") %>%
  set_table_properties(width = .5, layout = "autofit")
```

@@

```{r sitables5}
si_table.05.0$`_data` %>% 
  add_column(.after = 5,"empty1" = "") %>% 
  flextable() %>% 
  width("empty1", width = .2) %>% 
  set_header_labels(iv = "", empty1 = "") %>% 
  add_header_row(
    values = c(" ", "Task Version", " ", "Adversity Exposure"),
    colwidths = c(1, 4, 1, 4)
  ) %>% 
  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
  align(i = 1:2, align = "center", part = "header") %>% 
  border_remove() %>% 
  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = c(2), border.bottom = fp_border_default(), part = "body") %>% 
  bold(i = 1:2, part = "header") %>% 
  fontsize(size = 11, part = "body") %>%
  set_table_properties(width = .75, layout = "autofit")
```
